Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft

### 2024-05-02 docs/_tex/index.tex
adding Ana's comments

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Draft -- Discriminating Seagrasses From Green Macroalgae in France and Portugal Intertidal areas using high resolution multispectral drone imagery -- Draft},
  pdfauthor={Simon Oiry; Bede Ffinian Rowe Davies; Ana I. Sousa; Philippe Rosa; Maria Laura Zoffoli; Guillaume Brunier; Pierre Gernez; Laurent Barillé},
  pdfkeywords={Drone, Remote Sensing, Seagrass, Coastal
Ecosystems, Neural Network},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Draft -- Discriminating Seagrasses From Green Macroalgae in
France and Portugal Intertidal areas using high resolution multispectral
drone imagery -- Draft}
\author[1]{Simon Oiry%
\corref{cor1}%
}
 \ead{oirysimon@gmail.com} 
\author[1]{Bede Ffinian Rowe Davies%
%
}

>>>>

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft},
  pdfauthor={Simon Oiry; Bede Ffinian Rowe Davies; Ana I. Sousa; Philippe Rosa; Maria Laura Zoffoli; Guillaume Brunier; Pierre Gernez; Laurent Barillé},
  pdfkeywords={Drone, Remote Sensing, Seagrass, Coastal
Ecosystems, Neural Network},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Draft -- Discriminating Seagrasses From Green Macroalgae in
European Intertidal areas using high resolution multispectral drone
imagery -- Draft}
\author[1]{Simon Oiry%
\corref{cor1}%
}
 \ead{oirysimon@gmail.com} 
\author[1]{Bede Ffinian Rowe Davies%
%
}

### 2024-05-02 index.qmd
adding Ana's comments

title: Draft -- Discriminating Seagrasses From Green Macroalgae in France and Portugal Intertidal areas using high resolution multispectral drone imagery -- Draft

@@

brdr1 <- fp_border_default(color = "black", width = 1.5)
brdr2 <- fp_border_default(color = "grey", width = 1.5)
brdr3 <- fp_border_default(color = "grey40", width = 1.5)

>>>>

title: Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft

@@

brdr1 <- fp_border_default(color = "black", width = 1)
brdr2 <- fp_border_default(color = "grey", width = 1.5)
brdr3 <- fp_border_default(color = "grey40", width = 1.5)
